\section{Conclusion}

Coding agents were built to write code. But the capabilities required to write software---executing programs, managing files, searching the web, connecting to tools, reasoning about complex systems---turn out to be the capabilities required for \textit{everything}.

We formalized this as the \textbf{Meta-Agent Paradigm}: coding agents are meta-agents whose capability set subsumes virtually all domain-specific AI agents. We proposed \textbf{Agent Redirection}---specializing meta-agents through declarative Markdown templates rather than SDK-based construction---and demonstrated $\sim$300$\times$ reduction in development effort across four domains.

Our system, \textbf{SandAgent}, implements this paradigm with pluggable runtimes and sandboxes. On GAIA, template-redirected agents achieve competitive performance. The industry convergence---GitHub Agent HQ unifying Claude, Codex, and Copilot as interchangeable runtimes---provides independent validation.

We proposed the \textbf{AGI-Runtime Hypothesis}: that general intelligence will emerge not from a single model, but from the combination of capable models with agent runtimes that provide environmental grounding. The Meta-Agent Paradigm is the architectural pattern enabling this trajectory.

\begin{center}
\large
\textit{Coding agents are all you need.\\Don't build agents. Redirect them.}
\end{center}

\textbf{Availability.} SandAgent is open-source under Apache 2.0 at \url{https://github.com/vikadata/sandagent}.
