\begin{thebibliography}{25}

\bibitem[Andreessen(2011)]{andreessen2011software}
M.~Andreessen.
Why software is eating the world.
\textit{The Wall Street Journal}, 2011.

\bibitem[Anthropic(2025a)]{anthropic2025claude}
Anthropic.
Claude Code: An agentic coding tool.
\url{https://docs.anthropic.com/en/docs/claude-code}, 2025.

\bibitem[Anthropic(2024)]{anthropic2024mcp}
Anthropic.
Model Context Protocol.
\url{https://modelcontextprotocol.io}, 2024.

\bibitem[OpenAI(2025)]{openai2025codex}
OpenAI.
Codex CLI: Open-source coding agent.
\url{https://github.com/openai/codex}, 2025.

\bibitem[GitHub(2025)]{github2025copilot}
GitHub.
GitHub Copilot agent mode.
\url{https://github.com/features/copilot}, 2025.

\bibitem[GitHub(2026)]{github2026agenthq}
GitHub.
Agent HQ: Claude and Codex now available in public preview.
\url{https://github.blog/changelog/2026-02-04-claude-and-codex-in-agent-hq/}, 2026.

\bibitem[VS~Code(2026)]{vscode2026multiagent}
Visual Studio Code.
Your home for multi-agent development.
\url{https://code.visualstudio.com/blogs/2026/02/05/multi-agent-development}, 2026.

\bibitem[Mialon et~al.(2023)]{mialon2023gaia}
G.~Mialon, C.~Fourrier, C.~Swift, T.~Wolf, Y.~LeCun, and T.~Scialom.
GAIA: A benchmark for general AI assistants.
\textit{arXiv preprint arXiv:2311.12983}, 2023.

\bibitem[Jimenez et~al.(2024)]{jimenez2024swebench}
C.~E.~Jimenez, J.~Yang, A.~Wettig, S.~Yao, K.~Pei, O.~Press, and K.~Narasimhan.
SWE-bench: Can language models resolve real-world GitHub issues?
\textit{arXiv preprint arXiv:2310.06770}, 2024.

\bibitem[Wu et~al.(2023)]{wu2023autogen}
Q.~Wu, G.~Bansal, J.~Zhang, Y.~Wu, B.~Li, E.~Zhu, L.~Jiang, X.~Zhang, S.~Zhang, J.~Liu, et~al.
AutoGen: Enabling next-gen LLM applications via multi-agent conversation.
\textit{arXiv preprint arXiv:2308.08155}, 2023.

\bibitem[Hong et~al.(2023)]{hong2023metagpt}
S.~Hong, M.~Zhuge, J.~Chen, X.~Zheng, Y.~Cheng, C.~Zhang, J.~Wang, Z.~Wang, S.~K.~S.~Yau, Z.~Lin, et~al.
MetaGPT: Meta programming for a multi-agent collaborative framework.
\textit{arXiv preprint arXiv:2308.00352}, 2023.

\bibitem[LangChain(2023)]{langchain2023}
LangChain.
Building applications with LLMs.
\url{https://www.langchain.com}, 2023.

\bibitem[CrewAI(2024)]{crewai2024}
CrewAI.
Framework for orchestrating role-playing AI agents.
\url{https://www.crewai.com}, 2024.

\bibitem[E2B(2024)]{e2b2024}
E2B.
Cloud sandboxes for AI agents.
\url{https://e2b.dev}, 2024.

\bibitem[DaytimeAI(2025)]{agentbay2025}
DaytimeAI.
AgentBay: A hybrid interaction sandbox for seamless human-AI intervention.
\textit{arXiv preprint arXiv:2512.04367}, 2025.

\bibitem[Agent~Sandbox(2025)]{agentsandbox2025}
Agent Sandbox Contributors.
Agent Sandbox: A Kubernetes primitive for AI agent execution.
\url{https://github.com/agent-sandbox/agent-sandbox}, 2025.

\bibitem[Various(2025a)]{codeagentsurvey2025}
A survey on code generation with LLM-based agents.
\textit{arXiv preprint arXiv:2508.00083}, 2025.

\bibitem[Various(2025b)]{agenticprogramming2025}
AI agentic programming: A survey of techniques, challenges, and opportunities.
\textit{arXiv preprint arXiv:2508.11126}, 2025.

\bibitem[Various(2025c)]{multiagentcomm2025}
A communication-centric survey of LLM-based multi-agent systems.
\textit{arXiv preprint arXiv:2502.14321}, 2025.

\bibitem[WebProNews(2026)]{agentnative2026}
How AI agents are rewriting the rules of software development.
\url{https://www.webpronews.com/the-agent-native-revolution/}, 2026.

\bibitem[Sandock(2025)]{sandock2025}
Sandock.
Sandboxes in Docker for AI agents.
\url{https://sandock.ai}, 2025.

\bibitem[Sierra(2024)]{taubench2024}
Sierra Research.
$\tau$-bench: A benchmark for tool-agent-user interaction in real-world domains.
\textit{NeurIPS}, 2024.

\bibitem[Zhou et~al.(2024)]{webarena2024}
S.~Zhou, F.~F.~Xu, H.~Zhu, X.~Zhou, R.~Lo, A.~Sridhar, X.~Cheng, T.~Bisk, D.~Fried, U.~Alon, and G.~Neubig.
WebArena: A realistic web environment for building autonomous agents.
\textit{ICLR}, 2024.

\bibitem[Xie et~al.(2024)]{osworld2024}
T.~Xie, D.~Zhang, J.~Chen, X.~Li, S.~Zhao, R.~Cao, T.~J.~Hua, Z.~Cheng, D.~Shin, F.~Lei, Y.~Liu, and Y.~Tao.
OSWorld: Benchmarking multimodal agents for open-ended tasks in real computer environments.
\textit{NeurIPS}, 2024.

\bibitem[Liu et~al.(2023)]{agentbench2023}
X.~Liu, H.~Yu, H.~Zhang, Y.~Xu, X.~Lei, H.~Lai, Y.~Gu, H.~Ding, K.~Men, K.~Yang, et~al.
AgentBench: Evaluating LLMs as agents.
\textit{ICLR}, 2024.

\bibitem[Vaswani et~al.(2017)]{vaswani2017attention}
A.~Vaswani, N.~Shazeer, N.~Parmar, J.~Uszkoreit, L.~Jones, A.~N.~Gomez, {\L}.~Kaiser, and I.~Polosukhin.
Attention is all you need.
\textit{Advances in Neural Information Processing Systems}, 30, 2017.

\bibitem[OpenAI(2023)]{openai2023gpt4}
OpenAI.
GPT-4 technical report.
\textit{arXiv preprint arXiv:2303.08774}, 2023.

\end{thebibliography}
